Discrete Quantum Theories and Computing

### 2018-11-13 dissertation.tex
dissertation.lyx Adding TODOs

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
Given a finite sample space~$\Omega$ representing all possible outcomes,
and its power set $2^{\Omega}$ as the classical event space, a classical
probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
specifying how likely one of the outcome~$\omega\in E$ actually
happens. To maintain the coherence, we want $\mu$ subject to the
following constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
$\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.

In the quantum case, the events of interest are specified by \emph{projection
operators} $P$ satisfying the condition $P^{2}=P$. These include
the empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\Phi}$ where $\ket{\Phi}$ is a pure
quantum state (an element of a Hilbert space $\mathcal{H}$), sums
of \emph{orthogonal} projectors~$P_{0}$ and~$P_{1}$ with $P_{0}P_{1}=\mathbb{0}$,
and products of \emph{commuting} projectors $P_{0}$ and~$P_{1}$
with $P_{0}P_{1}=P_{1}P_{0}$. In a quantum probability space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
the set of all events is the set of all projectors on a given Hilbert
space denoted by $\events$. After the measurement, if the system
transits to a state $\ket{\Phi}$ and we call an event $P\in\events$
happen when .

each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
using a probability measure $\mu:\events\rightarrow\left[0,1\right]$
subject to the following constraints:
\begin{align}
\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
\end{align}
and for each pair of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability
assignment for every projector $P$, we can define the expectation
value of an observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
as \cite{544199,Jaeger2007}: 
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
\end{equation}
where the subscript $\mu$ might be omitted if it is clear according
to the context.

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current pure unnormalized quantum
state $\ket{\Phi}\in\mathcal{H}$; then the Born rule induces a probability
measure $\muB_{\Phi}$ defined as 
\begin{equation}
\muB_{\Phi}(P)=\frac{\melem{\Phi}{P}{\Phi}}{\ip{\Phi}{\Phi}}\,.\label{eq:Born}
\end{equation}
If $\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. For mixed states $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$,
where $\ket{\Phi_{j}}\in\mathcal{H}$ are normalized, $q_{j}>0$,
and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule induces a
probability measure $\muB_{\rho}$ defined as \cites{Born1983}{Mermin2007}{Jaeger2007}
\begin{equation}
\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)\,.\label{eq:mixed-Born}
\end{equation}

@@

A conventional quantum probability measure can be easily constructed
from a state $\rho$ according to the Born rule; conversely, this
is the only way to obtain a conventional quantum probability measure
according to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

@@

Our generalization of quantum probability measures to QIVPMs allows
us to strengthen the scope of one of the fundamental theorems of quantum
physics: the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
Our finite-precision extension of that theorem will suggest a resolution
to the debate initiated by Meyer and Mermin on the relevance of the
Kochen-Specker to experimental, and hence finite-precision, quantum
measurements \cites{PhysRevLett.83.3751}{HKSS1999}{Mermin1999}{Kent1999}{SimonBruknerZeilinger2001}{Cabello2002}{Larsson2002}{Appleby2002}{BarrettKent2004}{Appleby_2005}{Spekkens2005}{GuehneKleinmannCabelloEtAl2010}{MazurekPuseyKunjwalEtAl2016}.
Specifically, the original Kochen-Specker theorem is formulated using
a model quantum mechanical system that has \emph{definite values at
all times}~\cite{Held2016}, i.e., its observables have infinitely
precise values at all times. Our interval-valued probability framework
will allow us to state, and prove, a stronger version of the theorem
that holds even if the observables have values that are only definite
up to some precision specified by a parameter $\delta$. Our approach
provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
\begin{quote}
\ldots although the outcomes deduced from such imperfect measurements
will occasionally differ dramatically from those allowed in the ideal
case, if the misalignment is very slight, the statistical distribution
of outcomes will differ only slightly from the ideal case. 
\end{quote}

@@

\chapter{Further Discussion}

Almost all QIVPMs in Chapter~\ref{chap:QIVPM} are closely related
to quantum probability measures. For example, given a $\delta$-deterministic
QIVPM, Lemma~\ref{lemma:delta2zero} provides a way to derive a $0$-deterministic
QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
provides an systemic way to derive QIVPMs from quantum probability
measures.

>>>>

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
Given a finite sample space~$\Omega$ representing all possible outcomes,
and its power set $2^{\Omega}$ as the classical event space, a classical
probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
specifying how likely one of the outcome in $E$ actually happens.
To maintain the coherence, we want $\mu$ subject to the following
constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
$\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.

In the quantum case, the events of interest are specified by \emph{projection
operators} $P$ satisfying the condition $P^{2}=P$. These include
the empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\Phi}$ where $\ket{\Phi}$ is a pure
quantum state (an element of a Hilbert space $\mathcal{H}$), sums
of \emph{orthogonal} projectors~$P_{0}$ and~$P_{1}$ with $P_{0}P_{1}=\mathbb{0}$,
and products of \emph{commuting} projectors $P_{0}$ and~$P_{1}$
with $P_{0}P_{1}=P_{1}P_{0}$. In a quantum probability space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
the set of all events is the set of all projectors on a given Hilbert
space denoted by $\events$. \todo{Use the same idea as the classical
probability measure to explain the meaning of $\mu\left(P\right)$.}
each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
using a probability measure $\mu:\events\rightarrow\left[0,1\right]$
subject to the following constraints:
\begin{align}
\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
\end{align}
and for each pair of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability
assignment for every projector $P$, we can define the expectation
value of an observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
as \cite{544199,Jaeger2007}: 
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
\end{equation}
where the subscript $\mu$ might be omitted if it is clear according
to the context.

\todo{Rewrite the beginng of this paragraph to explain the meaning
of the Born rule... Maybe move Gleason's Theorem here?} A conventional
quantum probability measure can easily be constructed using the Born
rule if one knows the current pure unnormalized quantum state $\ket{\Phi}\in\mathcal{H}$;
then the Born rule induces a probability measure $\muB_{\Phi}$ defined
as 
\begin{equation}
\muB_{\Phi}(P)=\frac{\melem{\Phi}{P}{\Phi}}{\ip{\Phi}{\Phi}}\,.\label{eq:Born}
\end{equation}
If $\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. For mixed states $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$,
where $\ket{\Phi_{j}}\in\mathcal{H}$ are normalized, $q_{j}>0$,
and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule induces a
probability measure $\muB_{\rho}$ defined as \cites{Born1983}{Mermin2007}{Jaeger2007}
\begin{equation}
\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)\,.\label{eq:mixed-Born}
\end{equation}

@@

\todo{Make the meaning of Gleason's Theorem more clear? So that we
can explain the motivation of the question in Chapter~\ref{chap:Further-Discussion}}
A conventional quantum probability measure can be easily constructed
from a state $\rho$ according to the Born rule; conversely, this
is the only way to obtain a conventional quantum probability measure
according to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

@@

Our generalization of quantum probability measures to QIVPMs allows
us to strengthen the scope of one of the fundamental theorems of quantum
physics: the Kochen-Specker theorem \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}.
Our finite-precision extension of that theorem will suggest a resolution
to the debate initiated by Meyer and Mermin on the relevance of the
Kochen-Specker to experimental, and hence finite-precision, quantum
measurements . Specifically, the original Kochen-Specker theorem
is formulated using a model quantum mechanical system that has \emph{definite
values at all times}~\cite{Held2016}, i.e., its observables have
infinitely precise values at all times. Our interval-valued probability
framework will allow us to state, and prove, a stronger version of
the theorem that holds even if the observables have values that are
only definite up to some precision specified by a parameter $\delta$.
Our approach provides a quantitative realization of Mermin's intuition~\cite{Mermin1999}: 
\begin{quote}
\ldots although the outcomes deduced from such imperfect measurements
will occasionally differ dramatically from those allowed in the ideal
case, if the misalignment is very slight, the statistical distribution
of outcomes will differ only slightly from the ideal case. 
\end{quote}

@@

\chapter{Further Discussion\label{chap:Further-Discussion}}

\todo{After updating Sec.~\ref{sec:fuzzy}, update this chapter
by starting from the meaning of Gleason's Theorem.} Almost all QIVPMs
in Chapter~\ref{chap:QIVPM} are closely related to quantum probability
measures. For example, given a $\delta$-deterministic QIVPM, Lemma~\ref{lemma:delta2zero}
provides a way to derive a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
provides an systemic way to derive QIVPMs from quantum probability
measures.
